Forecasting the 2024 US Presidential Election: A Poll-of-Polls Approach to Predict the Outcome

### 2024-11-01 paper/paper.qmd
update the abstract

---
title: "Forecasting the 2024 US Presidential Election: A Poll-of-Polls Approach to Predict the Outcome"
subtitle: "Utilizing Poll Aggregation and Statistical Modeling to Project a Clear Path for the Presidential Race"
author: 
  - Ruiying Li
  - Lorina Yang
thanks: "Code and data are available at: https://github.com/Lorina-Y/US-Presidential-election.git."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Forecasting the 2024 US Presidential Election: A Poll-of-Polls Approach to Predict the Outcome"
subtitle: "Utilizing Poll Aggregation and Statistical Modeling to Project a Clear Path for the Presidential Race"
author: 
  - Ruiying Li
  - Lorina Yang
thanks: "Code and data are available at: https://github.com/Lorina-Y/US-Presidential-election.git."
date: today
date-format: long
abstract: "This paper forecasts the 2024 U.S. Presidential election by analyzing polling data on support for Kamala Harris and Donald Trump. Using Bayesian linear and logistic regression models, we examine the impact of poll characteristics like sample size and quality on support levels and predict each candidate’s winning probability. Our results show minimal influence from poll quality on support percentages but highlight a recent surge in Harris’s support, narrowing Trump’s previous lead. These findings provide insight into polling reliability and evolving voter sentiment as the election nears."
format: pdf
number-sections: true
bibliography: references.bib
---
